---
title: "What is Data Science?"
author: "Dr. Williams"
institute: "GATO365 Learning Center"
date: "April 6, 2022"
output:
  xaringan::moon_reader:
    # css: "pfs_css.css"
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

<!-- cChange font titles sizes -->

<!-- <style type="text/css"> -->
<!-- .remark-slide-content p, ul, ol, li { -->
<!-- font-size: 19px; -->
<!-- padding: 0.25em 0.25em 0.25em 0.25em; -->
<!-- } -->
<!-- .remark-slide-content  { -->
<!-- font-size: 28px; -->
<!-- padding: 0.5em 0.5em 0.5em 0.5em; -->
<!-- } -->
<!-- </style> -->


```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
library(tidyverse)
library(scales)
mono_light(
  base_color = "#3B4A68",
  header_font_google = google_font("Comic Sans MS"),
  text_font_google   = google_font("Comic Sans MS"),
  code_font_google   = google_font("Comic Sans MS"),
  background_image = 'logo2021_close.PNG',
  background_size = '75px',
  background_position = 'top 10px right 15px',
  title_slide_background_image = "none"
)
```

## How I went above the odds?

#### I am currently a data scientist that analyzes how students learn (make it sound appeasing)

--

#### - Undergraduate
#### - Graduate School
#### - Current Job

---

### So what can I do with data science?

#### - Social Media & Entertainment
#### - Sports
#### - Fashion

---

## Why are visualizations so important?

#### - Easiest way to get into data science
#### - Discover Patterns
#### - Communicate your conclusions


---

## What else is needed?
&
## How can you prepare now?

1. Context & Ethics
2. Mathematics (work extremely hard)
3. Programming (2 AP courses)
4. Statistics (1 AP course)




---

## Who wants to start today?

How many of you all can see yourself as a data scientists?

 - lets get you prepared 
 - who knows Billie Ellish, Kendrick LaMar, Cold Play, Pharrell Williams
 - Let's learn about music

---

```{r echo=FALSE}
df = data.frame(x = c(0,1), y = c(0,1))
p1 = df %>% 
  ggplot(aes(x = x, y = y)) +
  geom_blank() +
  geom_vline(xintercept = 0,size = 1) +
  geom_hline(yintercept = 0.5,size = 1) +
  scale_x_continuous(limits = c(-1,1), 
                     expand = c(0, 0),
                     labels = label_number(accuracy = 0.1)) +
  scale_y_continuous(limits = c(0,1), expand = c(0, 0))  +
  theme_bw() +
  theme(axis.title = element_text(size = 18, face = 'bold'))

```


## What is Valence?

#### Valence measures the natural **attractiveness/goodness (positive valence)** or **aversiveness/badness (negative valence)** of an event, object, or situation. 

--

```{r fig.align="center", echo = FALSE,fig.width = 8, out.width = '500px'}
p2 <- p1 +
  labs(x = 'Valence') +
  theme(axis.title.y = element_blank(),
        axis.line.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 18, face = 'bold'),
        plot.margin = margin(0.1, 0.5, 0.1, 0.5, "cm")
  ) 
p2
```


---

## That Good Feeling

```{r fig.align="center", echo = FALSE,fig.width = 8, out.width = '500px'}
p3 <- p2 +
  geom_rect(aes(xmin=0, xmax=1, ymin=0, ymax=1),alpha = 0.2, fill = 'blue') +
  annotate("text", x=0.5, y=0.5, label= "Good Feeling",size = 13, color = 'white') +
  theme(legend.position = 'none')
p3 
```


---

## Bad Feelings

```{r fig.align="center", echo = FALSE,fig.width = 8, out.width = '500px'}
p3 +
  geom_rect(aes(xmin=-1, xmax=0, ymin=0, ymax=1),alpha = 0.2, fill = 'red') +
  annotate("text", x=-0.5, y=0.5, label= "Bad Feeling",size = 13, color = 'white') +
  theme(legend.position = 'none')

```

---

### Energy!


```{r fig.align="center", echo = FALSE,fig.width = 8, out.width = '500px'}
p4 <- p1 +
  geom_rect(aes(xmin=-1, xmax=0, ymin=0, ymax=1),alpha = 0.2, fill = 'red') +
  geom_rect(aes(xmin=0, xmax=1, ymin=0, ymax=1),alpha = 0.2, fill = 'blue') +
  labs(x = 'Valence',y='Energy') +
  theme(axis.text = element_text(size = 12, face = 'bold'),
        plot.margin = margin(0.3, 0.5, 0.1, 0.5, "cm")
  )

p4
```


---

### Different Modes 
There are 4 mood were are going to consider
--

### **Sad** |  **Chill** | **Anger** | **Happy**

**Which quadrant should each mood be in?**

```{r fig.align="center", echo = FALSE,fig.width = 8, out.width = '400px'}
p4 +
  annotate("text", x=-0.5, y=0.25, label= "1",size = 15.5, color = 'white') +
  annotate("text", x=0.55, y=0.25, label= "4",size = 15.5, color = 'white') +
  annotate("text", x=-0.5, y=0.75, label= "2",size = 15.5, color = 'white') +
  annotate("text", x=0.55, y=0.75, label= "3",size = 15.5, color = 'white')
```

---

### Answer
```{r fig.align="center", echo = FALSE,fig.width = 8, out.width = '400px'}
p4 +
  annotate("text", x=-0.5, y=0.25, label= "Sad",size = 15.5, color = 'white') +
  annotate("text", x=0.55, y=0.25, label= "Chill",size = 15.5, color = 'white') +
  annotate("text", x=-0.5, y=0.75, label= "Anger",size = 15.5, color = 'white') +
  annotate("text", x=0.55, y=0.75, label= "Happy",size = 15.5, color = 'white')
```
