---
title: "Untitled"
author: "Dr. Williams"
date: "3/28/2022"
output: html_document
---


Step 1: Go [here](https://developer.spotify.com/dashboard/login) to find your ID and SECRET. You will have to log in using your Spotify information. Remember do save this information in the cloud, store on your laptop

Step 2: Install spotifyr by running the following code:

```{r eval=FALSE}
install.packages('spotifyr')
```


Step 3: You will have to run this with your ID and SECRET

```{r}
library(tidyverse)
library(spotifyr)
library(lubridate)
Sys.setenv(SPOTIFY_CLIENT_ID = 'XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX')
Sys.setenv(SPOTIFY_CLIENT_SECRET = 'XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX')
access_token <- get_spotify_access_token()
```



There are many things that you can do with *spotifyr*. I will provide a few 
examples but if you want more information go to the following [website](https://www.rdocumentation.org/packages/spotifyr/versions/2.1.1), look through page as well as towards the bottom that explains all the functions you now have access to.


## 3 examples of Using this function

### 1. Explore an artist
I love Old Kanye West and I try to understand New "Ye". So lets look (analyze) at all of his songs.

```{r}
kanye_west_df <- get_artist_audio_features('kanye west') 

kd = kanye_west_df%>% distinct(track_name, .keep_all= TRUE)
```
It takes a while because he has a lot of songs!

There are 39 variables that include various songs metrics such as:

- danceability, 
- energy
- key
- loudness
- mode
- speechiness
- acousticness
- instrumentalness             
- liveness 
- valence
- tempo

Spotify has various ways of measuring some of these variables and this [website](https://www.theverge.com/tldr/2018/2/5/16974194/spotify-recommendation-algorithm-playlist-hack-nelson) does a decent job of explaining this variables.

There are other variables that identify the song and album. You can spend 
sometime using this information to understand some of your artists. 

Other important variables include

- duration_ms: duration in milliseconds
- explicit: TRUE or FALSE if there explicit language (a good variable to look into)
- album_release_date and album_release_year: can used to know when some songs were released to the public
- track_name: the most important, is the name of the song

There are other worthwhile variables to look into but these stick out the most to me. 


One thing to note: There are some songs that are duplicated. There are many reasons for why there are duplicated songs. A reason relates to various artists, according to the [community page](https://community.spotify.com/t5/iOS-iPhone-iPad/Duplicates-of-the-same-albums/td-p/4542505) for Spotify, there seems to be an issue with artist reloading their music. Other reasons for duplicates include different versions of a song, for example, clean vs explicit, or different versions of the same song.

```{r}
kanye_west_df %>% 
  filter(track_name == 'Jesus Walks') %>% 
  select(track_name,explicit)
```

```{r}


kanye_west_df %>% 
  filter(track_name == 'Addiction') %>% 
  select(track_name,explicit,available_markets)
```
This last  example is an issue with where certain songs can be produced. This post will not spend time on this. 


We are going to explore old Kanye Top 20 hits from this [post](https://www.highsnobiety.com/p/best-kanye-west-songs/). I do not nescarily agree with this list but we will analyze it anyway.


“Diamonds From Sierra Leone”


```{r}
cd_df = kanye_west_df %>% 
  filter(album_name == 'The College Dropout')
```



The only big difference I notice is that the key names are some other metrics. We are going to randomly select a row and 


So now lets analyze!


*Vague Question:* Has the number of explicit tracks change over time?
*More Precise Question:* Has the number of explicit tracks relative to number of song produce in by year change over time?
```{r}
num_explict_songs_df = kanye_west_df %>% 
  group_by(album_release_year) %>% 
  summarise(number_explict = sum(explicit))
num_explict_songs_df
```






### 2. Explore a genre

```{r}
get_genre_artists(genre = 'country',limit = 25)
```


### 3. Example exploring your profile

```{r}
get_my_top_artists_or_tracks()
```














## List of 100 Songs


### Get 5 genres, 20 artists/songs per genre
1. Country
2. Hip Hop
3. Jazz
4. RnB
5. Pop

```{r}
## Get Artists
country_df = get_genre_artists(genre = 'country',limit = 25) %>% mutate()
hip_hop_df = get_genre_artists(genre = 'hip-hop',limit = 25)
jazz_df = get_genre_artists(genre = 'jazz',limit = 25)
rnb_df = get_genre_artists(genre = 'r&b',limit = 25)
pop_df = get_genre_artists(genre = 'pop',limit = 25)
```


```{r}
## Bind 
music_df = bind_rows(country_df,hip_hop_df,jazz_df,rnb_df,pop_df) %>% 
  filter(duplicated(name) == FALSE)
```



```{r}


##----------------------------------
## Name: gather_popular_songs
## Purpose: gather artist information from various functions
## Input: artist id
## Output: gather characteristics of artists
##----------------------------------
gather_popular_songs = function(artist_id){
  
  if( artist_id != c('2PaZWGu5T5nHjY2xxAkFsT')){
    # Sys.sleep(2)
    ## Gather Song Data
    song_df = get_artist_top_tracks(id = artist_id) %>% 
      filter(popularity == max(popularity)) %>% 
      arrange(album.release_date) %>% 
      filter(row_number() == 1)
    
    ## Gather Song data
    artist_df = song_df[[1]][[1]][1,2:3]
    
    ## Change Column Names
    colnames(artist_df) = c('artist_id','artist_name')
    
    # Sys.sleep(2)
    
    
    ## Gather Characteristics about Songs
    track_char_df = get_artist_audio_features(artist = artist_df$artist_name) %>% 
      filter(track_id == song_df$id) %>% 
      arrange(album_release_date) %>% 
      select(danceability,energy,loudness,speechiness,
             acousticness,instrumentalness,liveness,valence,tempo) %>% 
      filter(row_number() == 1)
    
    cat(artist_df$artist_name, '\n')
    
    ## Combine Data Fame Information
    final_df = bind_cols(song_df,artist_df,track_char_df)
  }
}

```



```{r}


artist_ids = music_df$id[-c(79,47)] ## Remove a song 
df = map_df(artist_ids, gather_popular_songs)
```


```{r}
saveRDS(df, file="topArtistsSongs.RData")
saveRDS(music_df, file="artists.RData")
```

